PANCHANGE_data_preprocessing

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
Cleaned up script for push

#Data level groups
Identify which data (prepan, retro and baseline) each participant has
Has only prepandemic == 0
prepandemic and baseline == 1
prepandemic, baseline, and retrospective == 2
++KT: not sure how best to categorise here so this may need some revision. 
```{r data level groups}
dat.glad <- dat.glad %>%
  mutate(
    data_group_full_numeric =
      case_when(
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0  & na_per_person_gad_retro == 0 & na_per_person_pcl_retro == 0 ~ 5,
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_pcl_retro == 0 ~ 4, #in GLAD, in COPING and have no missing PCL-retro items
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_gad_retro == 0 ~ 3, #in GLAD, in COPING and have no missing GAD-retro items
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0 ~ 2, #in GLAD, in COPING and have no missing PHQ-retro items
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) ~ 1,
        !is.na(startDate.glad) & is.na(startDate.coping.glad) ~ 0
      )
  )

>>>>

#Data level groups
Identify which data (prepan, retro and baseline) each participant has.
++KT: not sure how best to categorise here so this may need some revision. 
```{r data level groups}
dat.glad <- dat.glad %>%
  mutate(
    data_group_full_numeric =
      case_when(
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0  & na_per_person_gad_retro == 0 & na_per_person_pcl_retro == 0 ~ 5,
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_pcl_retro == 0 ~ 4, #in GLAD, in COPING and have no missing PCL-retro items
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_gad_retro == 0 ~ 3, #in GLAD, in COPING and have no missing GAD-retro items
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0 ~ 2, #in GLAD, in COPING and have no missing PHQ-retro items
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) ~ 1,
        !is.na(startDate.glad) & is.na(startDate.coping.glad) ~ 0
      )
  )
